emissions_by_gas

### 2022-10-24 r-examples/emissions_by_gas.Rmd
examples

---
title: "Emissions 2109"
author: "Johann Salzmann"
output: pdf_document
---

@@

rm(list = ls(envir = globalenv()),envir = globalenv())

if (!require("pacman")) install.packages("pacman")
library(pacman)

p_load(tidyr)
p_load(dplyr)
p_load(magrittr)
p_load(purrr)
p_load(stringr)
p_load(rlang)
p_load(tidyverse)
p_load(ggplot2)
p_load(readxl)

"%cin%" = function(x,y){str_detect(y,x)}
"%xin%" = function(x,y){x %cin% y | y %cin% x}
"%ni%" = Negate("%in%")
"%nci%" = Negate("%cin%")
"%nxi%" = Negate("%xin%")
"%.%" = function(x,y){paste(x,y,sep = "")}
cNA = as.character(NA)
as.numeric.factor = . %>% as.numeric(levels(.))[.]

@@

load("Data/data_wdi.RData")
data_ghg = read_excel(path ='Data/essd_ghg_data_gwp100.xlsx', sheet = 3)

data_ghg %<>% group_by(ISO,country,year) %>%
  summarise(GHGa = sum(GHG))

data_wdi %<>% select(ISO,year,pop)

data_joined = data_ghg %>% inner_join(data_wdi,by=c("ISO","year")) %>%
  mutate(GHGpc = GHGa/pop)

data_joined %>% filter(GHGpc > 20) %>%
  ggplot(aes(x=year, y=GHGpc, group=ISO)) +
  geom_line(aes(color=factor(ISO)))+
  geom_point() +
  theme_light()

data_joined %>% filter(year == 2019) %>%
  ggplot(aes(x=GHGpc)) +
  geom_histogram(bins=50) +
  theme(legend.position="none") +
  theme_light()

data_joined %>% filter(year == 2019) %>%
  ggplot(aes(x=GHGpc)) +
  geom_histogram(bins=50) +
  theme(legend.position="none") +
  theme_light()

data_joined %>% filter(year == 2019) %>%
  ggplot(aes(x=GHGpc)) +
  geom_density() +
  theme(legend.position="none") +
  theme_light()

data_joined %>% ggplot(aes(x=year, y=GHGpc, fill=ISO)) + 
    geom_area() +
    theme(legend.position="none")

>>>>

---
title: "emissions_by_gas"
author: "William F. Lamb"
output: pdf_document
---

@@

## At the start of a notebook you need to load all the packages needed for your analysis

library(tidyverse) ## In our case we need Tidyverse
library(readxl) ## And a library to open xlsx files

## We also need to get the data.
## There are two sheets already in the data folder
## These are sourced from a file online (https://zenodo.org/record/6483002)
## To load the data, we need to simply indicate where the file is ("xlsxFile =")
## And which sheet should be read ("sheet = ")

data_ghg <- read_excel(path ='Data/essd_ghg_data_gwp100.xlsx', sheet = 3)
data_lulucf <- read_excel(path = 'Data/essd_lulucf_data.xlsx', sheet = 2)

@@
